SIG Proceedings Paper in LaTeX Format

### 2019-08-28 SAC/submission/ACM_SigConf_SAC2020-2020_1.0/sample-sigconf.tex
abstract reworked

\begin{abstract}
The Skip-Gram Model with negative sampling (SGNS) is a simple and effective algorithm to create word embeddings. SGNS uses Stochastic Gradient Descent (SGD) as it's learning algorithm. While a lot of effort has gone into increasing the throughput of words of the SGNS, not much work has gone into optimizing the convergence time. Therefore, our work focuses on the latter. We propose a new batched version of the SGNS.  . Here are the components used to evaluate our work: to train our model we used the text8 dataset - to measure the quality of our word embeddings we used the wordsim353 dataset, which assess that similar words have vector represenations that are close to each other. To improve the quality of our batched version, we only allowed each word to appear once in a batch. Furthermore we deleted every word that appear more frequently than the 99 percentile. The advanced optimizer Adam combined with our batched approach outperformed the current state of the art implementation Gensim. Adam converged to a similarity value of 0.66 (state of the art) in 1 epochs, while Gensim took 4 epochs. Hence, this work shows that our batched version with advanced optimizers, and the deletion of outliers do decrease the convergence time of the SGNS. These results must be confirmed with other datasets, but optimizing our model in terms of throughput has the potential of further reducing the overall run time of the SGNS.

>>>>

\begin{abstract}
The Skip-Gram Model with negative sampling (SGNS) is a simple and effective algorithm to create word embeddings. SGNS uses Stochastic Gradient Descent (SGD) as it's optimizer. While a lot of effort has gone into increasing the throughput of words of the SGNS, not much work has gone into optimizing the convergence time. Therefore, our work focuses on the latter. We propose a new batched version of the SGNS. To improve the quality of our batched version, we only allowed each word to appear once in a batch. Furthermore we deleted every word that appear more frequently than the 99 percentile in our datasets.  Finally we also used advanced optimizers and input shuffling to decrease the convergence time. Here are the components used to evaluate our work: to train our model we used the text8 dataset - to measure the quality of our word embeddings we used the wordsim353 dataset, which assess that similar words have vector represenations that are close to each other. The advanced optimizer Adam combined with our batched approach outperformed the current state of the art implementation Gensim. Adam converged to a similarity value of 0.66 (state of the art) in 1 epoch, while Gensim took 4 epochs. Hence, this work shows that our batched version with advanced optimizers, and the deletion of outliers do decrease the convergence time of the SGNS. These results must be confirmed with other datasets, but optimizing our model in terms of throughput has the potential of further reducing the overall run time of the SGNS.
